\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electrons

### 2025-03-13 TilingProjectDraft/tilingProject.tex
added channel decoupling discussion

Let \(S^\pm\) be the set of momentum states in a small window around nodes along \(k_x = \pm k_y\). As discussed immediately above, the Kondo spin-exchange term close to the transition does not lead to scattering of any \(k-\)state from \(S^+\) to \(S^-\). This is captured by the following simplified Hamiltonian:
\begin{equation}\begin{aligned}\label{twoChannel}
H_\text{eff} = H(S^+) + H(S^-);~H(S) = \sum_{{\bf q}\in S,\sigma}\varepsilon_{\bf q}c^\dagger_{{\bf q}\sigma}c_{{\bf q}\sigma} + \sum_{{\bf q}_1\in S,{\bf q}_2\in S}\sum_{\alpha,\beta}J^*({\bf q}_1,{\bf q}_2){\bf S}_d\cdot {\bf \sigma}_{\alpha\beta}c^\dagger_{{\bf q}_1\alpha}c_{{\bf q}_2\beta}~,
\end{aligned}\end{equation}
where \(H(S^\pm)\) represents the dynamics of momentum states residing in regions \(S^\pm\). The only source of information transfer between the two regions is the fact that they interact with the same impurity local moment.

@@

\subsection{Entanglement entropy and Mutual information}
\begin{figure}[htpb]
	\includegraphics[width=0.24\textwidth]{S_k-1.pdf}
	\includegraphics[width=0.24\textwidth]{S_k-2.pdf}
	\includegraphics[width=0.24\textwidth]{S_k-3.pdf}
	\includegraphics[width=0.24\textwidth]{S_k-4.pdf}
\end{figure}
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.24\textwidth]{I2_k_N-1.pdf}
	\includegraphics[width=0.24\textwidth]{I2_k_N-2.pdf}
	\includegraphics[width=0.24\textwidth]{I2_k_N-3.pdf}
	% \includegraphics[width=0.24\textwidth]{I2_k_N-4.pdf}
\end{figure}

>>>>

Let \(S^\pm\) be the set of momentum states in a small window around nodes along \(k_x = \pm k_y\). As discussed immediately above, the Kondo spin-exchange term close to the transition does not lead to scattering of any \(k-\)state from \(S^+\) to \(S^-\). This is verified by calculating the ratio \(\text{max}\left\{ J_{k^+_1, k^-_2} \right\} / \text{max}\left\{ J_{k^+_1, k^+_2} \right\}\), where the maximum in the numerator is calculated from all the low-energy (fixed point) Kondo scattering processes that connect the two sets \(S^\pm\), while the denominator maximum is from within the set \(S^+\). This ratio vanishes (Fig.~\ref{channelDecoupling}) within the local pseudogap regime, indicating that no direct Kondo scattering process persists between the two sectors \(S^\pm\) at low energies, deep within the pseudogap regime.

\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.45\textwidth]{quadrantMaxKondo-49.pdf}
	\caption{}
	\label{channelDecoupling}
\end{figure}

This is captured by the following simplified Hamiltonian:
\begin{equation}\begin{aligned}\label{twoChannel}
H_\text{eff} = H(S^+) + H(S^-);~H(S) = \sum_{{\bf q}\in S,\sigma}\varepsilon_{\bf q}c^\dagger_{{\bf q}\sigma}c_{{\bf q}\sigma} + \sum_{{\bf q}_1\in S,{\bf q}_2\in S}\sum_{\alpha,\beta}J^*({\bf q}_1,{\bf q}_2){\bf S}_d\cdot {\bf \sigma}_{\alpha\beta}c^\dagger_{{\bf q}_1\alpha}c_{{\bf q}_2\beta}~,
\end{aligned}\end{equation}
where \(H(S^\pm)\) represents the dynamics of momentum states residing in regions \(S^\pm\). The only source of information transfer between the two regions is the fact that they interact with the same impurity local moment.

@@

\subsection{Entanglement entropy and Mutual information}
\begin{figure}[htpb]
	\includegraphics[width=0.24\textwidth]{S_k-1.pdf}
	\includegraphics[width=0.24\textwidth]{S_k-3.pdf}
	\includegraphics[width=0.24\textwidth]{S_k-4.pdf}
	\includegraphics[width=0.24\textwidth]{S_k-5.pdf}
\end{figure}
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.24\textwidth]{I2_k_N-1.pdf}
	\includegraphics[width=0.24\textwidth]{I2_k_N-3.pdf}
	\includegraphics[width=0.24\textwidth]{I2_k_N-4.pdf}
	\includegraphics[width=0.24\textwidth]{I2_k_N-5.pdf}
\end{figure}
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.24\textwidth]{I2_k_edge-1.pdf}
	\includegraphics[width=0.24\textwidth]{I2_k_edge-3.pdf}
	\includegraphics[width=0.24\textwidth]{I2_k_edge-4.pdf}
	\includegraphics[width=0.24\textwidth]{I2_k_edge-5.pdf}
\end{figure}
